Reporte de inventario de eviencias

### 2021-10-13 Latex/journal_v1/research plan/main.tex
add research plan

\subsection{Reliability of URLLC}
As we know, UEs request URLLC services, require services with low latency.
For the M/M/1 system, the probability of the delay for each application $s$ in the UPF, CU, DU and RU is as follow, respectively
P_r\{T_{UPF}^{s} \geq T_{UPF}^{max}\} &= e^{-(\mu_u - \alpha_{s}/{M_s^{u}})T_{UPF}^{max}}\\
P_r\{T_{CU}^{s} \geq T_{CU}^{max}\} &= e^{-(\mu_c - \alpha_{s}/{M_s^{c}})T_{CU}^{max}}\\
P_r\{T_{DU}^{s} \geq T_{DU}^{max}\} &= e^{-(\mu_d - \alpha_{s}/{M_s^{d}})T_{DU}^{max}}\\
P_r\{T_{RU}^{s} \geq T_{RU}^{max}\} &= e^{-(R_{{tot}_s} - \alpha_{s})T_{RU}^{max}}\\
So the probability of coincidence of these events is as follow
P_r\{E_1, E_2, E_3, E_4\} = A_1 A_2 A_3 A_4,
Where $E_1 = T_{UPF}^{s} \geq T_{UPF}^{max}$, $E_2 =T_{CU}^{s} \geq T_{CU}^{max} $, $E_3 =T_{DU}^{s} \geq T_{DU}^{max} $ and $E_4 =T_{RU}^{s} \geq T_{RU}^{max} $.
Also $A_1=e^{-(\mu_u - \alpha_{s}/{M_s^{u}})T_{UPF}^{max}}$, $A_2=e^{-(\mu_c - \alpha_{s}/{M_s^{c}})T_{CU}^{max}}$, $A_3= e^{-(\mu_d - \alpha_{s}/{M_s^{d}})T_{DU}^{max}}$ and $A_4 = e^{-(R_{{tot}_s} - \alpha_{s})T_{RU}^{max}}$.

@@

Where, $z_d$ is shown that whether the $d^{th}$ DC is active or not and $\psi_d$ is a static cost when a DC is active, i.e.,

@@

Where, $\phi_s^u$, $\phi_s^c$ and $\phi_s^d$ are the static cost of energy in UPF, CU and DU, respectively. 
So the optimization problem is formulated as follow.
In the large-time scale the aim of the paper is to minimize the power of the system with the presence constraints
\begin{subequations}

@@

\min\limits_{ \boldsymbol{M}, \boldsymbol{Y}, \boldsymbol{E} } \phi_{tot}   \quad &   \ \\

@@

 &\mathcal{R}_{u_{(s_1,i)}} \geq  \mathcal{R}_{min}^{s} \quad \forall s, \label{c13} \\
& \phi_{tot}  \leq \phi_{max}, \label{c19} \\
& \sum_{s=1}^{S}\sum_{i=1}^{U_s}R_{u_{(s,k)}}^r \leq C_{max}^r \quad \forall r, \label{c15}\\ 
 &\textstyle \sum_{s=1}^{S} y_{s,d} \bar{\Omega}_{\mathfrak{z},s}^{tot}  \leq   \tau_{\mathfrak{z}_d} 
 \quad \forall d, \forall \mathfrak{z}\in \mathcal{E}; \label{c20}

@@

In the small-time scale the aim of this paper is to maximize the sum rate of UEs  of eMBB services, minimum the delay of UEs of URLLC services, and minimum the power mMTC services with the presence of constraints.
\begin{subequations}
\max\limits_{\boldsymbol{P}, \boldsymbol{E}, \boldsymbol{G} }   \quad &  \sum_{s=1}^{S_1}\sum_{i=1}^{U_s}R_{u_{(s,k)}}^e - \sum_{s=1}^{S_2}T^s_{tot} - \sum_{s=1}^{S_3}\sum_{i=1}^{U_s} p_{u_{(s,k)}} \ \\
&\mathcal{R}_{u_{(s_1,i)}} \geq  \mathcal{R}_{min}^{s} \quad \forall s, \label{c13} \\
& \sum_{s=1}^{S}\sum_{i=1}^{U_s}R_{u_{(s,k)}}^r \leq C_{max}^r \quad \forall r, \label{c15}\\ 
&T_{tot}^s \leq T_{tot}^{max,s} \quad \forall s,\label{c16} \\
& P_r\{E_1, E_2, E_3, E_4\} \leq \epsilon_s \quad \forall s_2, \label{c166}\\
& g^r_{u(s,i)} \leq g^r_{u(s,i)}\sum_{k =1}^{K_s} e^{k}_{r,u(s,i)}  \quad \forall s,i , \label{c18} \\
where $\boldsymbol{P} =[p_{u(s,i)}] \:\: \forall s , \forall i $, is the matrix of power for UEs,
$\boldsymbol{E} =[e_{r,u(s,i)}^k] \:\: \forall s , \forall i \forall r, \forall k$ indicate the binary variable for PRB association. Moreover, $\boldsymbol{G} =[g_{u(s,i)}^r] \:\: \forall s , \forall i \forall r$ is a binary variable for O-RU association. Furthermore, $M = [M_s^d, M_s^c, M_s^u] \:\: \forall s$ is the matrix that shown the number of VNFs in each layer of slice and $\boldsymbol{Y} =[y_{s,d}]  \:\: \forall s ,  \forall d $ is a binary variable shown whether

@@

Also, $\eta$ is weighted variable to value between the benefit and the cost term of objective function.
\eqref{c11}, and \eqref{c12}, indicate that the power of each RU do not exceed the maximum power, and the power of each UE is a positive integer value, respectively. 
Also \eqref{c13}  shows that the rate of each UE requesting eMBB, URLLC and mMTC is more than a threshold, respectively.
\eqref{c15} and \eqref{c16} expressed the limited capacity of the fronthaul link, and the limited delay of receiving signal, respectively.
\eqref{c16} is a reliability condition that the delay in each layer should be less than threshold.
 \eqref{c18} guarantee that if a UE in admitted by the system, O-RU and PRB is associated to it, respectively.
In addition, \eqref{c19} indicate that the static cost of energy of VNFs in each slice do not exceed from the threshold. 
Moreover, in \eqref{c20}  $\mathcal{E} = \{M,S,C, N\}$ and the constraint supports
that we have enough physical resources for VNFs of each slice.

@@

@@

  $\mathbb{E}$ represented the statistical average. 
 Based on the Bellman equation we have
 \begin{equation}
	V^{\Pi}(s) = \mathbb{E}_{\Pi,P}[R+\gamma V^{\Pi}(s')]
\end{equation}  
 and also, 
   \begin{equation}
  	Q^{\Pi}(s,a) = \mathbb{E}_{\Pi,P}[R+\gamma Q^{\Pi}(s',a')]
  \end{equation}  
  Where, $s'$ and $a'$ can be obtained from $\Pi(.|s')$ and $P(.|s,a)$.
The goal of reinforcement learnin is to obtain the optimal policy to maximize the $Q^{\Pi}(s,a)$.
So, using Bellman equation, we have
\begin{equation}
	Q^{*}(s,a) = \mathbb{E}_{\Pi^*,P}[R+\gamma Q^{*}(s',a')].
\end{equation} 
Also, $T^*$ is the Bellman operator
\begin{equation}
	T^{*}Q(s,a) = \mathbb{E}_{\Pi^*,P}[R+\gamma Q(s',a')]
\end{equation} 
By using this operator iteratively, 
$Q_{t+1}(s,a) \leftarrow T^{*}Q(s,a) $
the algorithm can converge
$Q_{t}(s,a) \rightarrow Q^*(s,a)$.
 $t \rightarrow \infty $
\cite{montague1999reinforcement,gan1}.
In the Q-learning in each episode we have
\begin{equation}
	Q(s_{t+1},a_{t+1}) = Q(s_t,a_t)+\alpha[ r_{t+1} + \gamma \max_{a \in A}{Q(s_{t+1},a)}-Q(s_t,a_t)]
\end{equation}
where, $\alpha$ is the learning rate.
\subsection{Preliminary Numerical Results}
Here, we simplify the large-time scale problem and indicate the numerical results.
The numerical results for this problem (which is the VNF placement) can be shown as follow. 
\begin{subequations}
	\begin{alignat}{4}
		\min\limits_{\boldsymbol{Y} }   \quad &   \psi_{tot}(\boldsymbol{Y})(t)\\
		\text{s. t.} \quad & \textstyle \sum_{d=1}^{D_c} y_{s,d}(t) \geq 1 \quad \forall s, \\
		&\textstyle  \sum_{s=1}^{S} y_{s,d}(t) \bar{\Omega}_{s}^{tot}  \leq   \tau_{d} \quad  \forall d, \forall ;  \label{eqomega}
	\end{alignat}
\end{subequations}
Suppose we have just one limited resource (CPU in each server). The ratio of the number of the used-servers  with the optimal method to the used-servers with the Q-learning method based on time spent can be shown as figure \ref{fig:dynamicEpoch2}. In this figure, after about 900 epochs, the algorithm converges to the 0.9 of optimal solution.
\begin{figure}[H]
	\centering
	\includegraphics[scale = 0.4]{./fig/ratio_episode2} %[width=\linewidth] 
	\caption{   The ratio of the number of servers used with the optimal method to the servers used using the reinforcement learning method based on time spent}
	\label{fig:dynamicEpoch2}
\end{figure}
Figure \ref{fig:consumptionE}, shows the ratio of the normalized cost to the average number of slices required in the optimal state and the reinforcement learning algorithm.
\begin{figure}[H]
	\centering
	\includegraphics[scale = 0.4]{./fig/consumptionE} %[width=\linewidth] 
	\caption{  The ratio of the normalized cost to the average number of cuts required in the optimal state and the reinforcement learning algorithm }
	\label{fig:consumptionE}
\end{figure}
\section{Research Plan}
The table below outlines the goals and six-month planning overall.
\begin{table}
 \caption {Research Plan} \label{table:1a}
 \begin{center}
  \begin{tabular}{||c c ||}
  \hline
Month & Tasks \\ [0.5ex]
  \hline\hline
  First Month & Complete the System model for the Intelligent RAN slicing\\
  \hline
  Second Month & Find the best method for this system model \\
  \hline
  Third Month & Generalized this method for other system models \\
  \hline
    Fourth Month & Obtain Numerical Results\\
  \hline
    Fifth Month & Write the paper\\
  \hline
      Sixth Month & Review the paper\\
  \hline
 \end{tabular}
 \end{center}
 \end{table}

>>>>

%\subsection{Reliability of URLLC}
%As we know, UEs request URLLC services, require services with low latency.
%For the M/M/1 system, the probability of the delay for each application $s$ in the UPF, CU, DU and RU is as follow, respectively
%\begin{split}
%P_r\{T_{UPF}^{s} \geq T_{UPF}^{max}\} &= e^{-(\mu_u - \alpha_{s}/{M_s^{u}})T_{UPF}^{max}}\\
%P_r\{T_{CU}^{s} \geq T_{CU}^{max}\} &= e^{-(\mu_c - \alpha_{s}/{M_s^{c}})T_{CU}^{max}}\\
%P_r\{T_{DU}^{s} \geq T_{DU}^{max}\} &= e^{-(\mu_d - \alpha_{s}/{M_s^{d}})T_{DU}^{max}}\\
%P_r\{T_{RU}^{s} \geq T_{RU}^{max}\} &= e^{-(R_{{tot}_s} - \alpha_{s})T_{RU}^{max}}\\
%\end{split}
%So the probability of coincidence of these events is as follow
%P_r\{E_1, E_2, E_3, E_4\} = A_1 A_2 A_3 A_4,
%where $E_1 = T_{UPF}^{s} \geq T_{UPF}^{max}$, $E_2 =T_{CU}^{s} \geq T_{CU}^{max} $, $E_3 =T_{DU}^{s} \geq T_{DU}^{max} $ and $E_4 =T_{RU}^{s} \geq T_{RU}^{max} $.
%Also $A_1=e^{-(\mu_u - \alpha_{s}/{M_s^{u}})T_{UPF}^{max}}$, $A_2=e^{-(\mu_c - \alpha_{s}/{M_s^{c}})T_{CU}^{max}}$, $A_3= e^{-(\mu_d - \alpha_{s}/{M_s^{d}})T_{DU}^{max}}$ and $A_4 = e^{-(R_{{tot}_s} - \alpha_{s})T_{RU}^{max}}$.

@@

where, $z_d$ is shown that whether the $d^{th}$ DC is active or not and $\psi_d$ is a static cost when a DC is active, i.e.,

@@

where, $\phi_s^u$, $\phi_s^c$ and $\phi_s^d$ are the static cost of energy in UPF, CU and DU, respectively.
Here, we want to maximize the energy efficiency $\eta$. 
So the optimization problem is formulated as follow

\begin{subequations} \label{mainP}

@@

\max\limits_{ \boldsymbol{M}, \boldsymbol{Y}, \boldsymbol{E},\boldsymbol{P},\boldsymbol{G} } &\eta = \frac{\sum_{s=1}^{S_1}\sum_{i=1}^{U_s}R_{u_{(s,k)}}}{\phi_{tot} +P_r}       \ \\

@@

 &\mathcal{R}_{u_{(s,i)}} \geq  \mathcal{R}_{min}^{s} \quad \forall s, \label{c13} \\
 &\textstyle \sum_{s=1}^{S} y_{s,d} \bar{\Omega}_{\mathfrak{z},s}^{tot}  \leq   \tau_{\mathfrak{z}_d}, \quad  \mathcal{E} = \{M,S,C, N\}, \label{c14}\\
&p_{r,u(s,i)}^{k}  \leq P_{s}^{max}  \quad \forall i,\forall r,\forall s, \forall k,\label{c12-1} \\
%&\mathcal{R}_{u_{(s_2,i)}}^u \geq  \mathcal{R}_{min}^{s_2,u} \quad \forall s_2, \label{c14} \\
& C_r \leq C^{max}_r \quad \forall r, \label{c15}\\ 
&T^{\text{\text{tot}}}_{u(s,i)}  \leq T^{max}_{s} \quad \forall i,\forall s,\label{c16} \\
& \mu_s \geq \alpha_s/M_s \quad \forall s,\label{c16-1} \\
& \mathcal{R}_{u_{(s,i)}} \geq {\lambda}_{u_{(s,i)}} \quad \forall i,\forall s,\label{c16-2} \\
& 0 \leq M_s \leq M^{max}_s  \quad \forall s,\label{c16-3}\\
%& P_r\{E_1, E_2, E_3, E_4\} \leq \epsilon_s \quad \forall s_2, \label{c166}\\
& \sum_{r}g^r_{u(s,i)} = 1  \quad \forall s,\forall i, \label{c17}  \\
& \sum_{k =1}^{K_s} g^r_{u(s,i)} e^{k}_{r,u(s,i)} \geq 1  \quad \forall s,\forall i ,\forall r \label{c18-1} \\
& \sum_{s =1}^{S}\sum_{i=1}^{U_s}g^r_{u(s,i)} e^{k}_{r,u(s,i)} \leq 1  \quad \forall s,\forall i ,\forall r \label{c18} \\
& \phi^{\text{\text{tot}}}  \leq \phi^{max}, \label{c19} \\
& g^r_{u(s,i)} \in \{0,1\} \quad \forall s,\forall i, \label{c20}  \\
& e^k_{r,u(s,i)} \in \{0,1\} \quad \forall s,\forall i, \label{c21}  

@@

\noindent where $\boldsymbol{P} =[p_{r,u(s,i)}^{k}], \:\: \forall s , \forall i, \forall r, \forall k $, is the matrix of power for UEs, $\boldsymbol{E} =[e_{r,u(s,i)}^k], \:\: \forall s , \forall i, \forall r, \forall k$ indicate the binary variable for PRB association. Moreover, $\boldsymbol{G} =[g_{u(s,i)}^r], \:\: \forall s , \forall i, \forall r$ is a binary variable for O-RU association. Furthermore, $M = [M_s^d, M_s^c, M_s^u], \:\: \forall s$ is the matrix that shows the number of VNFs in each layer of slice.
Also $\boldsymbol{Y} =[y_{s,d}]  \:\: \forall s ,  \forall d $ is a binary variable shown whether

@@

\eqref{c11}, \eqref{c12} and \eqref{c12-1} indicate that the power of each O-RU does not exceed the maximum power, the power of each UE is a positive integer value, and the power of each UE in each service does not exceed the maximum power of each service, respectively.  
Also, \eqref{c13} shows that the rate of each UE requesting each type of service, i.e., eMBB, mMTC, and uRLLC, is more than a threshold, respectively.
\eqref{c15} and \eqref{c16} expressed the limited fronthaul capacity and the limited end-to-end delay of the received signal, respectively.
\eqref{c16-1} and \eqref{c16-2} denoted the stability of the M/M/1 queue model.
\eqref{c16-3} restricted the number of VNF in each slice due to the limited resources.
%\eqref{c16} is a reliability condition that the delay in each layer should be less than the threshold.
\eqref{c17} and \eqref{c18-1} guarantee that O-RU and PRB are associated with the UE, respectively.
Also, \eqref{c18} ensures that each PRB can not be assigned to more than one UE associated with the same O-RU.
In addition, \eqref{c19} indicates that the fixed cost of energy of VNFs in each slice does not exceed the threshold. 
Moreover, \eqref{c20} and \eqref{c21} depict that $\boldsymbol{E}$ and $\boldsymbol{G}$ are matrix of binary variables.
In addition, in \eqref{c14}, the constraint supports that we have enough physical resources for VNFs of each slice.

@@

Problem \eqref{mainP}, is a two-time scale problem, i.e., large time scale and small time scale. On a large-time scale, we aim to minimize the power of servers and obtain the QoS of slices. The assignment of PRB to slices is implemented in this time scale. In the small-time scale, the assignment of O-RU to UEs and the assignment of PRB of slices to UEs is executed, and the optimal power is obtained.

@@

  $\mathbb{E}$ represented the statistical average. 
 Based on the Bellman equation we have
 \begin{equation}
	V^{\Pi}(s) = \mathbb{E}_{\Pi,P}[R+\gamma V^{\Pi}(s')]
\end{equation}  
 and also, 
   \begin{equation}
  	Q^{\Pi}(s,a) = \mathbb{E}_{\Pi,P}[R+\gamma Q^{\Pi}(s',a')]
  \end{equation}  
  where, $s'$ and $a'$ can be obtained from $\Pi(.|s')$ and $P(.|s,a)$.
The goal of reinforcement learnin is to obtain the optimal policy to maximize the $Q^{\Pi}(s,a)$.
So, using Bellman equation, we have
\begin{equation}
	Q^{*}(s,a) = \mathbb{E}_{\Pi^*,P}[R+\gamma Q^{*}(s',a')].
\end{equation} 
Also, $T^*$ is the Bellman operator
\begin{equation}
	T^{*}Q(s,a) = \mathbb{E}_{\Pi^*,P}[R+\gamma Q(s',a')]
\end{equation} 
By using this operator iteratively, 
$Q_{t+1}(s,a) \leftarrow T^{*}Q(s,a) $
the algorithm can converge
$Q_{t}(s,a) \rightarrow Q^*(s,a)$.
 $t \rightarrow \infty $
\cite{montague1999reinforcement,gan1}.
In the Q-learning in each episode we have
\begin{equation}
	Q(s_{t+1},a_{t+1}) = Q(s_t,a_t)+\alpha[ r_{t+1} + \gamma \max_{a \in A}{Q(s_{t+1},a)}-Q(s_t,a_t)]
\end{equation}
where, $\alpha$ is the learning rate.
\subsection{Preliminary Numerical Results}
Here, we simplify the large-time scale problem and indicate the numerical results.
The numerical results for this problem (which is the VNF placement) can be shown as follow. 
\begin{subequations}
	\begin{alignat}{4}
		\min\limits_{\boldsymbol{Y} }   \quad &   \psi_{tot}(\boldsymbol{Y})(t)\\
		\text{s. t.} \quad & \textstyle \sum_{d=1}^{D_c} y_{s,d}(t) \geq 1 \quad \forall s, \\
		&\textstyle  \sum_{s=1}^{S} y_{s,d}(t) \bar{\Omega}_{s}^{tot}  \leq   \tau_{d} \quad  \forall d, \forall ;  \label{eqomega}
	\end{alignat}
\end{subequations}
Suppose we have just one limited resource (CPU in each server). The ratio of the number of the used-servers  with the optimal method to the used-servers with the Q-learning method based on time spent can be shown as figure \ref{fig:dynamicEpoch2}. In this figure, after about 900 epochs, the algorithm converges to the 0.9 of optimal solution.
\begin{figure}[H]
	\centering
	\includegraphics[scale = 0.4]{./fig/ratio_episode2} %[width=\linewidth] 
	\caption{   The ratio of the number of servers used with the optimal method to the servers used using the reinforcement learning method based on time spent}
	\label{fig:dynamicEpoch2}
\end{figure}
Figure \ref{fig:consumptionE}, shows the ratio of the normalized cost to the average number of slices required in the optimal state and the reinforcement learning algorithm.
\begin{figure}[H]
	\centering
	\includegraphics[scale = 0.4]{./fig/consumptionE} %[width=\linewidth] 
	\caption{  The ratio of the normalized cost to the average number of cuts required in the optimal state and the reinforcement learning algorithm }
	\label{fig:consumptionE}
\end{figure}
\section{Research Plan}
Table \ref{table:1a}, outlines the goals and six-month planning overall.
\begin{itemize}
\item Task 1: Complete the system model and problem formulation, 
\end{itemize}

\begin{table}
 \caption {Research Plan} \label{table:1a}
 \begin{center}
  \begin{tabular}{||c c ||}
  \hline
Month & Tasks \\ [0.5ex]
  \hline\hline
  First Month & Complete the System model for the Intelligent RAN slicing\\
  \hline
  Second Month & Find the best method for this system model \\
  \hline
  Third Month & Generalized this method for other system models \\
  \hline
    Fourth Month & Obtain Numerical Results\\
  \hline
    Fifth Month & Write the paper\\
  \hline
      Sixth Month & Review the paper\\
  \hline
 \end{tabular}
 \end{center}
 \end{table}
